Missing data: Current practice in football research and recommendations for improvement

### 2020-09-04 paper/paper.Rmd
alter search wording.

Of the 199 articles screened, 136 were deemed eligible, representing
\~10% of the articles found (Figure X). XX articles (of the 199) were
excluded due to not meeting the inclusion criteria. The proportion of
articles that reported missing data was 5.9% (95% confidence interval
X% to X%) or 8/136. Of the articles that did not mention missing data
(128/136), 7.1% (3.3% to 13.1%) or 9/128 shared their dataset, making
it difficult to determine whether there was any missingness. While the
absence of a missing data statement does not necessarily mean missing
data are not being reported, it does suggest that this aspect of the
analysis process receives little consideration -- especially in contrast
to many of the papers that included (potentially meaningless) tests of
normality (e.g., Kruskall-Wallis test).

>>>>

Of the 199 articles screened, 136 were deemed eligible, representing
\~10% of the articles found (Figure X). XX articles (of the 199) were
excluded due to not meeting the inclusion criteria. The proportion of
articles that reported missing data was 5.9% (95% confidence interval;
X% to X%) or 8/136. Of the articles that did not mention missing data
(128/136), 7.1% (3.3% to 13.1%) or 9/128 shared their dataset, making
it difficult to determine whether there was any missingness. While the
absence of a missing data statement does not necessarily mean missing
data are not being reported, it does suggest that this aspect of the
analysis process receives little consideration--especially in contrast
to many of the papers that included (potentially meaningless) tests of
normality (e.g., Kruskall-Wallis test).
